Graph-Based Neural Reconstruction \\ from Skeletonized 3D Networks

### 2017-11-15 papers/cvpr2018/0_introduction.tex
Updated related work and bib file
Removed Fig. 2

\begin{figure*}[t]
	\centering
	\subfloat[]{
	\includegraphics[width=.24\linewidth]{./figures/pipeline/image.png}
	}
	\subfloat[]{
	\includegraphics[width=.24\linewidth]{./figures/pipeline/affinities.png}
	}
	\subfloat[]{
	\includegraphics[width=.24\linewidth]{./figures/pipeline/watershed.png}
	}
	\subfloat[]{
	\includegraphics[width=.24\linewidth]{./figures/pipeline/neuroproof.png}
	}
	\caption{An overview of a pixel-based connectomics segmentation pipeline. (a) Original EM image data (b) Output of a CNN predicting voxel affinities (c) Clustering of the affinities using a watershed algorithm (d) Agglomeration of the super-voxels into larger segments.}
	\label{fig:pipeline}
\end{figure*}

@@

We present a \textit{top-down graph-based} method that builds on the outputs of bottom-up pixel-based segmentation approaches. We first extract 3D skeleton networks from the input segmentation (Fig.~\ref{fig:pipeline}) and generate a simplified 3D graph (Fig.~\ref{fig:teaser}a). We train a CNN classifier on the agglomerated regions in the segmentation data to detect errors. We run the classifier to populate the graph edge weights with error probabilities. We then use a graph optimization algorithm to partition the graph into the final improved reconstruction by enforcing domain-specific global constraints from biology (Fig.~\ref{fig:teaser}b).

>>>>

%\begin{figure*}[t]
%	\centering
%	\subfloat[]{
%	\includegraphics[width=.24\linewidth]{./figures/pipeline/image.png}
%	}
%	\subfloat[]{
%	\includegraphics[width=.24\linewidth]{./figures/pipeline/affinities.png}
%	}
%	\subfloat[]{
%	\includegraphics[width=.24\linewidth]{./figures/pipeline/watershed.png}
%	}
%	\subfloat[]{
%	\includegraphics[width=.24\linewidth]{./figures/pipeline/neuroproof.png}
%	}
%	\caption{An overview of a pixel-based connectomics segmentation pipeline. (a) Original EM image data (b) Output of a CNN predicting voxel affinities (c) Clustering of the affinities using a watershed algorithm (d) Agglomeration of the super-voxels into larger segments.}
%	\label{fig:pipeline}
%\end{figure*}

@@

We present a \textit{top-down graph-based} method that builds on the outputs of bottom-up pixel-based segmentation approaches. We first extract 3D skeleton networks from the input segmentation and generate a simplified 3D graph (Fig.~\ref{fig:teaser}a). We train a CNN classifier on the agglomerated regions in the segmentation data to detect errors. We run the classifier to populate the graph edge weights with error probabilities. We then use a graph optimization algorithm to partition the graph into the final improved reconstruction by enforcing domain-specific global constraints from biology (Fig.~\ref{fig:teaser}b).
